A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-07-19 paper/elsarticle/elsarticle-template.tex
paper

In practice, calibrating a camera relies on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output the calibration matrix~$\mathtt{K}$, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. To calibrate a camera, images of a calibration surface such as a chessboard pattern are used to identify the 2D-3D correspondences $\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\{\mathbf{X}_{i,j}\} = \{\mathbf{X}_{i,j'}\}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is used to obtain the calibration matrix~$\mathtt{K}$ and rigid body transformations $g = (\mathtt{R}_j, \mathbf{t}_j) \in SE(3)$ that minimize the reprojection error
\begin{equation}
\sum_{i,j} d\big(\mathbf{x}_{i,j}, \mathtt{K}(\mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j)\big),
\label{re}
\end{equation}
where $\mathbf{X}_{i,j}' = \mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j$ expresses $\mathbf{X}_i$ in the camera coordinate frame corresponding to the $j^{\text{th}}$ calibration image, $\mathtt{K}\mathbf{X}_{i,j}' \in \mathbb{R}^2$ gives the projection of $\mathbf{X}_{i,j}$ to that image, and $d$ is a distance function. The inverse rigid body transformation~$g^{-1}$ gives the pose of the $j^{\text{th}}$ camera relative to the static 3D points of the calibration pattern.

>>>>

In practice, calibrating a camera relies on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output the calibration matrix~$\mathtt{K}$, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. To calibrate a camera, images of a calibration surface such as a chessboard pattern are used to identify the 2D-3D correspondences $\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\{\mathbf{X}_{i,j}\} = \{\mathbf{X}_{i,j'}\}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is used to obtain the calibration matrix~$\mathtt{K}$ and rigid body transformations $g = (\mathtt{R}_j, \mathbf{t}_j) \in SE(3)$ that minimize the reprojection error
\begin{equation}
\sum_{i,j} d\big(\mathbf{x}_{i,j}, \mathtt{K}(\mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j)\big),
\label{re}
\end{equation}
where $\mathbf{X}_{i,j}' = \mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j$ expresses $\mathbf{X}_{i,j}$ in the camera coordinate frame corresponding to the $j^{\text{th}}$ calibration image, $\mathtt{K}\mathbf{X}_{i,j}' \in \mathbb{R}^2$ gives the projection of $\mathbf{X}_{i,j}$ to that image, and $d$ is a distance function. The inverse rigid body transformation~$g^{-1}$ gives the pose of the $j^{\text{th}}$ camera relative to the static 3D points of the calibration pattern.
